Family Income and Educational Returns in China, 2010-2020: Higher Returns Favor the Wealthy, but Gaps Hold Steady

### 2024-12-04 paper/paper.qmd
used styler

# Assign names to the list based on the filenames (without .rds)
names(models) <- tools::file_path_sans_ext(basename(model_files))

```

@@

# Data
data <- data.frame(
  `CFPS Year` = c(2020, 2018, 2016, 2014, 2012, 2010, "Temporal mean"),
  `Q1vsQ2` = c(0.9482, 0.2441, 0.7665, -2.3488, 1.2055, 0.4988, 0.2191),
  `Q1vsQ3` = c(1.9092, 2.3463, 1.2655, -1.1069, 0.9527, 3.0412, 1.4013),
  `Q1vsQ4` = c(4.1670, 3.9833, 4.5967, 0.6399, 3.1572, 5.6921, 3.7060),
  `Q2vsQ3` = c(1.2350, 1.7767, 1.2912, 0.2706, -0.0212, 2.1727, 1.1208),
  `Q2vsQ4` = c(3.1601, 3.3524, 3.9390, 3.3242, 3.7233, 4.9265, 3.7376),
  `Q3vsQ4` = c(2.2804, 3.7010, 3.1417, 3.1945, 4.4302, 2.1920, 3.1566),
  `Cross Sectional Mean` = c(2.2833, 2.5673, 2.5001, 0.6623, 2.2413, 3.0872, ' ')
)

# Create the table
kable(
  data,
  format = "latex"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down"), 
    position = "center",
    full_width = FALSE
  )

```
\FloatBarrier
Note: In 2012, educational returns for Q1, Q2, and Q3 were insignificant. In 2010, educational returns for Q1 and Q2 were insignificant.

@@

data <- data.frame(
  `CFPS Year` = c(2020, 2018, 2016, 2014, 2012, 2010),
  `Q1 Returns` = c('4.9507***', '4.1730**', '2.5671*', '4.4464**', '-1.0031', '0.1803'),
  `Q2 Returns` = c('5.8130***', '4.0239***', '3.0501***', '2.5357**', '0.0590', '1.1116'),
  `Q3 Returns` = c('7.3284***', '6.1466***', '4.1665***', '2.8027***', '0.4928', '3.9577***'),
  `Q4 Returns` = c('10.3891***', '9.1724***', '6.9051***', '6.3410***', '4.4870***', '8.0710***')
)

kable(
  data,
  format = "latex"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down"), 
    position = "center",
    full_width = FALSE
  )

```
\FloatBarrier
Significant codes: * = p < 0.05, ** = p < 0.01,  *** = p < 0.001

>>>>

# Assign names to the list based on the filenames (without .rds)
names(models) <- tools::file_path_sans_ext(basename(model_files))
```

@@

# Data
data <- data.frame(
  `CFPS Year` = c(2020, 2018, 2016, 2014, 2012, 2010, "Temporal mean"),
  `Q1vsQ2` = c(0.9482, 0.2441, 0.7665, -2.3488, 1.2055, 0.4988, 0.2191),
  `Q1vsQ3` = c(1.9092, 2.3463, 1.2655, -1.1069, 0.9527, 3.0412, 1.4013),
  `Q1vsQ4` = c(4.1670, 3.9833, 4.5967, 0.6399, 3.1572, 5.6921, 3.7060),
  `Q2vsQ3` = c(1.2350, 1.7767, 1.2912, 0.2706, -0.0212, 2.1727, 1.1208),
  `Q2vsQ4` = c(3.1601, 3.3524, 3.9390, 3.3242, 3.7233, 4.9265, 3.7376),
  `Q3vsQ4` = c(2.2804, 3.7010, 3.1417, 3.1945, 4.4302, 2.1920, 3.1566),
  `Cross Sectional Mean` = c(2.2833, 2.5673, 2.5001, 0.6623, 2.2413, 3.0872, " ")
)

# Create the table
kable(
  data,
  format = "latex"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down"),
    position = "center",
    full_width = FALSE
  )
```
\FloatBarrier
Note: In 2012, educational returns for Q1, Q2, and Q3 were insignificant. In 2010, educational returns for Q1 and Q2 were insignificant.

@@

data <- data.frame(
  `CFPS Year` = c(2020, 2018, 2016, 2014, 2012, 2010),
  `Q1 Returns` = c("4.9507***", "4.1730**", "2.5671*", "4.4464**", "-1.0031", "0.1803"),
  `Q2 Returns` = c("5.8130***", "4.0239***", "3.0501***", "2.5357**", "0.0590", "1.1116"),
  `Q3 Returns` = c("7.3284***", "6.1466***", "4.1665***", "2.8027***", "0.4928", "3.9577***"),
  `Q4 Returns` = c("10.3891***", "9.1724***", "6.9051***", "6.3410***", "4.4870***", "8.0710***")
)

kable(
  data,
  format = "latex"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down"),
    position = "center",
    full_width = FALSE
  )
```
\FloatBarrier
Significant codes: * = p < 0.05, ** = p < 0.01,  *** = p < 0.001
